A thermodynamic view of dusty protoplanetary disks: axisymmetric stability

### 2016-10-18 appendix.tex
adding SI to main text

\section{Compressible streaming instability}\label{compressible_streaming}
We consider an unstratified disk with $\Phi = \Phi (r)$ so that $\p_zP = \p_z\rho =
0$. The background $\p_rP/\rho$ and $\tepsilon$ are constants. 
We Fourier analyze in $r$ and $z$ so that $\p_z\to \ii k_z$ and
$\p_r\to \ii k_x$ when acting on perturbations, and denote $|\bm{k}|^2
\equiv k_x^2 + k_z^2$. We neglect 
background gradients when compared with that of perturbations. The linearized
equations are, after eliminating the azimuthal velocity:

>>>>

\section{Dispersion relation in an unstratified isothermal dusty disk}\label{compressible_streaming}
We consider an unstratified disk with $\Phi = \Phi (r)$ so that $\p_zP = \p_z\rho =
0$. The background $\p_rP/\rho$ and $\tepsilon$ are constants. 
We Fourier analyze in $r$ and $z$ so that $\p_z\to \ii k_z$ and
$\p_r\to \ii k_x$ when acting on perturbations, and denote $|\bm{k}|^2
\equiv k_x^2 + k_z^2$. We neglect 
background gradients when compared with that of perturbations. The linearized
equations are, after eliminating the azimuthal velocity:

### 2016-10-18 linear.tex
adding SI to main text

Eq. \ref{lin_mass}---\ref{lin_energy} is a set of ordinary
differntial equations in $z$. All coefficients and amplitudes are
evaluated at a fiducial radius $r=r_0$, but their full $z$-dependence
is retained. Numerical solutions are generally required for the 
verticall-stratified problem, as we pursue below.

However, in the special case of an unstratified disk (neglecting the vertical
component of the stellar gravity), we may also Fourier analyze in $z$
to obtain a local dispersion relation. This is done in 
Appendix \ref{compressible_streaming}. There we show the above linearized
equations give the streaming instability in the appropriate limit 
\citep{youdin05a,jacquet11}.

%\subsection{Boundary conditions}

%Eq. \ref{lin_mass}---\ref{lin_energy} can be reduced to a set of
%first-order differential equations for $W, Q$ and $\dd v_z$. We can
%see this schematically as follows. Eq. \ref{lin_xmom} and
%\ref{lin_ymom} may be combined to yield 
%\begin{align*}
%  \dd v_r = \dd v_r (W, Q, \dd v_z). 
%\end{align*} 
%We can then take the continuity equation as an equation for $\dd v_z$, 
%\begin{align*}
%\text{Eq. \ref{lin_mass}} \Rightarrow \dd v_z^\prime(z) = \dd
%  v_z^\prime(W,Q,\dd v_z),
%\end{align*}
%and the vertical momentum equation as an equation for $Q$, 
%\begin{align*}
%\text{Eq. \ref{lin_zmom}} \Rightarrow Q^\prime(z) = 
% Q^\prime(W,Q,\dd v_z). 
%\end{align*}

>>>>

Eq. \ref{lin_mass}---\ref{lin_energy} is a set of ordinary
differntial equations in $z$. All coefficients and amplitudes are
evaluated at a fiducial radius $r=r_0$, but their full $z$-dependence
is retained. Numerical solutions are generally required for the 
verticall-stratified problem. We pursue this in \S\ref{results}

\section{Compressible streaming instability}  
In the special case of an unstratified disk (neglecting the vertical
component of the stellar gravity), we may also Fourier analyze in $z$
to obtain a local dispersion relation of the form 
$\sum_{j=1}^{5}c_j\sigma^j = 0$. 
This is done in 
Appendix \ref{compressible_streaming}.

There we show the above linearized
equations give the streaming instability in the appropriate limit 
\citep{youdin05a,jacquet11}.

\begin{deluxetable*}{llrrrrr}
  \tablecolumns{7}
  \tablecaption{Selected eigenfrequencies for the streaming
    instability. \label{bstar_compare}
  }
  \tablehead{
    \colhead{Mode} & 
    \colhead{$\tau_\mathrm{s}\OmK$} &
    \colhead{$\epsilon$} &
     \colhead{$K_x = K_z$} &
      \colhead{$\sigma/\OmK$ (two-fluid)} &
    \colhead{$\sigma/\OmK$ (one-fluid, Eq. \ref{streaming_dispersion})}   &
    \colhead{$\mathcal{W}$ (arbitrary units) } 
  }
\startdata
 linA, \cite{youdin07} &  $0.1$       & 3.0 & 30    & $-0.3480 +
 0.4190\ii$ & $0.3647 + 0.4251\ii$ & $0.196$\\

linB, \cite{youdin07} & $0.1$        &  0.2 & 6 & $0.4999 +
0.0154\ii$&   $-0.4999 + 0.0054\ii$  & $6.95$ \\

linC,  \cite{bai10b}  & $10^{-2}$   &  2.0 & 1500&   $0.1049 +
0.5981\ii$   &  $0.1344 + 0.6665\ii$  & $0.0198$\\

linD, \cite{bai10b} &  $10^{-3}$   &  2.0 & 2000 & $0.3225 +
0.3154\ii$& $0.3228 + 0.3155\ii$ &  $1.77\times10^{-3}$
\enddata
\end{deluxetable*}

%\subsection{Boundary conditions}
%Eq. \ref{lin_mass}---\ref{lin_energy} can be reduced to a set of
%first-order differential equations for $W, Q$ and $\dd v_z$. We can
%see this schematically as follows. Eq. \ref{lin_xmom} and
%\ref{lin_ymom} may be combined to yield 
%\begin{align*}
%  \dd v_r = \dd v_r (W, Q, \dd v_z). 
%\end{align*} 
%We can then take the continuity equation as an equation for $\dd v_z$, 
%\begin{align*}
%\text{Eq. \ref{lin_mass}} \Rightarrow \dd v_z^\prime(z) = \dd
%  v_z^\prime(W,Q,\dd v_z),
%\end{align*}
%and the vertical momentum equation as an equation for $Q$, 
%\begin{align*}
%\text{Eq. \ref{lin_zmom}} \Rightarrow Q^\prime(z) = 
% Q^\prime(W,Q,\dd v_z). 
%\end{align*}
